---
output:
  beamer_presentation:
    theme: metropolis
---
```{r config, include=FALSE}
library(gridExtra)
library(crotchet)
knitr::opts_chunk$set(echo=FALSE, results="hide", cache=TRUE)
```

# Warm up

\scriptsize

```python
import pathlib
import shutil
import zipfile


def extract_txt(zip_filename, dst_dir):
    """Extract all txt files from a zip."""
    with zipfile.ZipFile(zip_filename) as zip_src:
        names = [
            name for name in zip_src.namelist()
            if pathlib.Path(name).suffix == ".txt"
        ]
        for member in names:
            dst_path = pathlib.Path(dst_dir) / pathlib.Path(member).name
            with zip_src.open(member) as src, open(dst_path, "wb") as dst:
                shutil.copyfileobj(src, dst)
```

# Welcome to Madpy!

![The Madpy Magpy.](img/madpy-logo.pdf)

# Organizers

```{r organizers, fig.width=8, fig.height=8, out.height="80%", fig.cap="Pierce Edmiston, Dan Imhoff, Willy Hakizimana, and James Bourbeau."}
grid.arrange(
  read_image("img/pierce.jpg", width = 0.9, height = 0.9),
  read_image("img/dan.jpg", width = 0.9, height = 0.9),
  read_image("img/willy.jpg", width = 0.9, height = 0.9),
  read_image("img/james.jpg", width = 0.9, height = 0.9),
  nrow = 2
)
```

# Sponsor

```{r sponsor}
draw_image("img/heroku.png")
```

# Code of conduct

**Madpy is a community group** and open to all experience levels.  
We are committed to **a safe, professional environment.**  
**Questions and comments** supporting the speaker are encouraged.  
**Interruptions and criticisms** of the speaker are not.

[github.com/madison-python/code-of-conduct](https://github.com/madison-python/code-of-conduct)

# Want more Madpy?

[**madpy.com**](https://madpy.com)  
[meetup.com/madpython](https://www.meetup.com/madpython/)  
[github.com/madison-python](https://github.com/madison-python)  
[github.com/madison-python/welcome](https://github.com/madison-python/welcome)

\bigskip

## Join us on Slack

\bigskip

`slack.madpy.com` to sign up.  
`madpy.slack.com` to sign in.

\bigskip

## Subscribe to our googlegroups

\bigskip

Send a blank email to: `madpy+subscribe@googlegroups.com`

# Madpy meetings

```{r bread, fig.cap="Bread."}
grid.arrange(
  read_image("img/bread.png", width=0.9),
  read_image("img/lannister-debts.png", width=0.9),
  nrow = 1,
  widths = c(0.37, 0.63)
)
```

# Data Driven Wisconsin

```{r data-driven-wi}
grid.arrange(
  read_image("img/data-driven-wi-pierce.jpg", width = 0.9),
  read_image("img/data-driven-wi-james.jpg", width = 0.9),
  nrow = 1
)
```

# Madpy calendar

- August 8: Python Data Model (Josh Karpel)
- _September 5:_ Numba (James Bourbeau)
- October 10: Hackathon - Kaggle Competition

# Fluent Python

[madpy.s3-us-west-2.amazonaws.com/ch01-data-model.pdf](https://madpy.s3-us-west-2.amazonaws.com/ch01-data-model.pdf)
