---
output:
  beamer_presentation:
    theme: metropolis
---
```{r config, include=FALSE}
library(gridExtra)
library(crotchet)
knitr::opts_chunk$set(echo=FALSE, results="hide", cache=TRUE)
```

# Welcome to Madpy!

![The Madpy Magpy.](img/madpy-logo.pdf)

# Organizers

```{r organizers, fig.cap="Pierce Edmiston, Dan Imhoff, and William Hakizimana."}
grid.arrange(
  read_image("img/pierce.jpg", width = 0.9),
  read_image("img/dan.jpg", width = 0.9),
  read_image("img/willy.jpg", width = 0.9),
  nrow = 1
)
```

# Sponsor

PerBlue

- [Senior Data Analyst](https://perblue.com/Careers.aspx#op-277104-senior-data-analyst)
- [Data Analyst](https://perblue.com/Careers.aspx#op-305962-data-analyst)
- [Software Developer (Front-End/Tools)](https://perblue.com/Careers.aspx#op-294641-software-developer-frontendtools)

\small Go to [github.com/madison-python/welcome](https://github.com/madison-python/welcome) for links.

# Code of conduct

**Madpy is a community group** and open to all experience levels.  
We are committed to **a safe, professional environment.**  
**Questions and comments** supporting the speaker are encouraged.  
**Interruptions and criticisms** of the speaker are not.

[github.com/madison-python/code-of-conduct](https://github.com/madison-python/code-of-conduct)

# Want more Madpy?

[meetup.com/madpython](https://www.meetup.com/madpython/)  
[github.com/madison-python](https://github.com/madison-python)  
[github.com/madison-python/welcome](https://github.com/madison-python/welcome)

\bigskip

## Join us on Slack

\bigskip

`slack.madpy.com` to sign up.  
`madpy.slack.com` to sign in.

\bigskip

## Subscribe to our googlegroups

\bigskip

Send a blank email to: `madpy+subscribe@googlegroups.com`

# Madpy meetings

```{r bread, fig.cap="Bread."}
grid.arrange(
  read_image("img/bread.png", width=0.9),
  read_image("img/lannister-debts.png", width=0.9),
  nrow = 1,
  widths = c(0.37, 0.63)
)
```

# Madpy calendar

- **March 14: Flask (Whil Hentzen)**
- April 11: Deploying a machine learning API (Devin Conathan)
- May 9: Zendesk!
- June 13: Python Environments (???)
- July 11: Python Data Model (Josh Karpel)

# Topics

**Vote one topic up in the queue, or append a new one.**

- lighting talks on hobby projects
- asyncio
- microservices
- python syntax
- metaclasses
- decorators
- C-extensions
- numba
- cupy