---
output:
  beamer_presentation:
    theme: metropolis
---
```{r config, include=FALSE}
library(gridExtra)
library(crotchet)
knitr::opts_chunk$set(echo=FALSE, results="hide", cache=TRUE)
```

# Welcome to Madpy!

![The Madpy Magpy.](img/madpy-logo.pdf)

# Organizers

```{r organizers, fig.cap="Pierce Edmiston and Dan Imhoff."}
grid.arrange(
  read_image("img/pierce.jpg", width = 0.9),
  read_image("img/dan.jpg", width = 0.9),
  nrow = 1
)
```

# Code of conduct

Madpy is a community group and open to everyone.  
We are committed to a safe, professional environment.  
Harassment or offensive behavior will not be tolerated.

[github.com/madison-python/code-of-conduct](https://github.com/madison-python/code-of-conduct)

# Want more Madpy?

[meetup.com/madpython](https://www.meetup.com/madpython/)  
[github.com/madison-python](https://github.com/madison-python)

\bigskip

## Join us on Slack

\bigskip

`slack.madpy.com` to sign up.  
`madpy.slack.com` to sign in.

\bigskip

## Subscribe to our googlegroups

\bigskip

Send a blank email to: `madpy+subscribe@googlegroups.com`

# Madpy meetings

```{r bread, fig.cap="Bread."}
draw_image("img/bread.png", width=0.25)
```

# Calendar

- **June 14: Intro to descriptors: Surprisingly simple (Jake Zimmerman)**
- **July 12: Advanced descriptors: I lied (Jake Zimmerman)**
- August 1/29: Pair Night?
- August 9: Django! (Willy Hakizimana)
- _September 6: Rust for Pythonistas (Josh Karpel)_
- _October 4: ?_
- _November 8: Ruby through a Python lens (Casey Brant)_
