---
output:
  beamer_presentation:
    theme: metropolis
---
```{r config, include=FALSE}
library(gridExtra)
library(crotchet)
knitr::opts_chunk$set(echo=FALSE, results="hide", cache=TRUE)
```

# Welcome to Madpy!

![The Madpy Magpy.](img/madpy-logo.pdf)

# Organizers

```{r organizers, fig.cap="Pierce Edmiston and Dan Imhoff."}
grid.arrange(
  read_image("img/pierce.jpg", width = 0.9),
  read_image("img/dan.jpg", width = 0.9),
  nrow = 1
)
```

# Code of conduct

Madpy is a community group and open to everyone. We are committed to a safe,
professional environment for everyone, and will not tolerate harassment or
offensive behavior.

[github.com/madison-python/code-of-conduct](https://github.com/madison-python/code-of-conduct)

# Want more Madpy?

[meetup.com/madpython](https://www.meetup.com/madpython/)  
[github.com/madison-python](https://github.com/madison-python)

## Join us on Slack

`slack.madpy.com` to sign up.  
`madpy.slack.com` to sign in.

## Subscribe to our googlegroups

Send a blank email to: `madpy+subscribe@googlegroups.com`

# Madpy meetings

```{r bread, fig.cap="Bread."}
draw_image("img/bread.png", width=0.25)
```

# Calendar

- **April 12: Deep learning in python (Devin Conathan)**
- **May 10: Data munging with pandas (Ed Rogers)**
- June 14: Intro to descriptors: Surprisingly simple (Jake Zimmerman)
- July 12: Advanced descriptors: I lied (Jake Zimmerman)
- August 9: Django! (Willy Hakizimana)
- August X: Pair Night?
