---
output:
  beamer_presentation:
    theme: metropolis
---
```{r config, include=FALSE}
library(knitr)
library(magrittr)
library(googlesheets)
library(gridExtra)
library(crotchet)

opts_chunk$set(echo=FALSE, results="hide", cache=TRUE)

responses <- gs_title("suggestion-box-responses", verbose = FALSE) %>%
  gs_read(verbose = FALSE)
title <- colnames(responses)[2]
```

# Welcome to Madpy!

![The Madpy Magpy.](img/madpy-logo.pdf)

# Organizers

```{r organizers, fig.cap="Pierce Edmiston and Dan Imhoff."}
grid.arrange(
  read_image("img/pierce.jpg", width = 0.9),
  read_image("img/dan.jpg", width = 0.9),
  nrow = 1
)
```

# Code of conduct

Madpy is a community group and is open to all. We are committed to a safe,
professional environment for everyone and will not tolerate harassment or
offensive behavior of any kind.

By being here, you accept to our Code of Conduct, which you can read
in its entirety here:

[github.com/madison-python/code-of-conduct](https://github.com/madison-python/code-of-conduct)

**Information listed in the CoC**

- Examples of positive and negative behaviors.
- Procedure for responding to harrassment or offensive behavior.
- Explanation of record keeping.

# Want more Madpy?

## Join us on Slack

`slack.madpy.com` to sign up.  
`madpy.slack.com` to sign in.

## Subscribe to our googlegroups

Send a blank email to: `madpy+subscribe@googlegroups.com`

# Madpy meetings

```{r bread, fig.cap="Bread."}
draw_image("img/bread.png", width=0.25)
```

# The suggestion box: [bit.ly/madpy-suggestions](https://bit.ly/madpy-suggestions)

```{r suggestions, results="asis"}
kable(responses[title])
```

# Calendar

- February 28: Pair Night!
- March 8: Machine learning with scikit-learn (James Bourbeau)
- April 12: Deep learning in python (Devin Conathan)
- May 10: Data munging with pandas (Ed Rogers)
- June 14: Intro to descriptors: Surprisingly simple (Jake Zimmerman)
- July 12: Advanced descriptors: I lied (Jake Zimmerman)
- August 9: Django! (Willy Hakizimana)

# Pair Night!

6p at Industrious  

Schedule of events:

- Show up and make a nametag.
- Find a project ([trello.com/madpy](https://trello.com/madpy)), find partner (or partners).
- Pair #1
- Pair #2

For more information, see [github.com/madison-python/pair-night](https://github.com/madison-python/pair-night).