---
output:
  beamer_presentation:
    theme: metropolis
---
```{r config, include=FALSE}
library(gridExtra)
library(crotchet)
knitr::opts_chunk$set(echo=FALSE, results="hide", cache=TRUE)
```

# Welcome to Madpy!

![The Madpy Magpy.](img/madpy-logo.pdf)

# Organizers

```{r organizers, fig.cap="Pierce Edmiston, Dan Imhoff, and William Hakizimana."}
grid.arrange(
  read_image("img/pierce.jpg", width = 0.9),
  read_image("img/dan.jpg", width = 0.9),
  read_image("img/willy.jpg", width = 0.9),
  nrow = 1
)
```

# Code of conduct

**Madpy is a community group** and open to all experience levels.  
We are committed to **a safe, professional environment.**  
**Questions and comments** supporting the speaker are encouraged.  
**Interruptions and criticisms** of the speaker are not.

[github.com/madison-python/code-of-conduct](https://github.com/madison-python/code-of-conduct)

# Want more Madpy?

[meetup.com/madpython](https://www.meetup.com/madpython/)  
[github.com/madison-python](https://github.com/madison-python)  
[github.com/madison-python/welcome](https://github.com/madison-python/welcome)

\bigskip

## Join us on Slack

\bigskip

`slack.madpy.com` to sign up.  
`madpy.slack.com` to sign in.

\bigskip

## Subscribe to our googlegroups

\bigskip

Send a blank email to: `madpy+subscribe@googlegroups.com`

# Madpy meetings

```{r bread, fig.cap="Bread."}
draw_image("img/bread.png", width=0.25)
```

# Recap

August 20: Intro to Python for Data workshop

# Annoucements

October 18: AllDayDevOps ([alldaydevops.com](https://alldaydevops.com))

# Madpy calendar

- **Pair programming Q&A | Rust for Pythonistas**
- **September 13: Pair Night**
- October 4: Polygot Bites Lightning talks
    - _Kotlin, Elm, Dot, Stata, underscore.js_
- November 8: Ruby through a Python lens (Casey Brant)
- December 13: Python Typings (Nick Hyatt)

# Pair Night recap

```{r pair-night-v1, fig.cap="Photo by @TyHitzeman."}
draw_image("img/pair-night-v1.jpg", width=0.25)
```

# Pair Night

Project ideas board:
: [trello.com/madpy](https://trello.com/madpy)

GitHub repo:
: [github.com/madison-python/pair-night](https://github.com/madison-python/pair-night)

RSVP to the Meetup event:
: [bit.ly/pair-night-v2](https://bit.ly/pair-night-v2)

# Pair Night Q&A

## Jim Remsik, @jremsikjr
