---
output:
  beamer_presentation:
    theme: metropolis
---
```{r config, include=FALSE}
library(knitr)
library(magrittr)
library(googlesheets)
library(gridExtra)
library(crotchet)

opts_chunk$set(echo=FALSE, results="hide", cache=TRUE)

responses <- gs_title("suggestion-box-responses", verbose = FALSE) %>%
  gs_read(verbose = FALSE)
title <- colnames(responses)[2]
```

# Welcome to Madpy!

![The Madpy Magpy.](img/madpy-logo.pdf)

# Organizers

```{r organizers, fig.cap="Pierce Edmiston and Dan Imhoff."}
grid.arrange(
  read_image("img/pierce.jpg", width = 0.9),
  read_image("img/dan.jpg", width = 0.9),
  nrow = 1
)
```

# Want more Madpy?

## Join us on Slack

`slack.madpy.com` to sign up.  
`madpy.slack.com` to sign in.

## Subscribe to our googlegroups

Send a blank email to: `madpy+subscribe@googlegroups.com`

# Madpy meetings

```{r bread, fig.cap="Bread."}
draw_image("img/bread.png", width=0.25)
```

# The suggestion box: [bit.ly/madpy-suggestions](https://bit.ly/madpy-suggestions)

```{r suggestions, results="asis"}
kable(responses[title])
```

# Calendar

- Pair Night!
- February 8: Generators part 2: promises and lazy evaluation (Ryan Prior)
- March 8: Machine learning with scikit-learn (James Bourbeau)
- April 12: Deep learning in python (Devin Conathan)
- May 10: Data munging with pandas (Ed Rogers?)
