---
output:
  beamer_presentation:
    theme: metropolis
---
```{r config, include=FALSE}
library(gridExtra)
library(crotchet)
knitr::opts_chunk$set(echo=FALSE, results="hide", cache=TRUE)
```

# Welcome to Madpy!

![The Madpy Magpy.](img/madpy-logo.pdf)

# Organizers

```{r organizers, fig.cap="Pierce Edmiston and Dan Imhoff."}
grid.arrange(
  read_image("img/pierce.jpg", width = 0.9),
  read_image("img/dan.jpg", width = 0.9),
  nrow = 1
)
```

# Code of conduct

Madpy is a community group and open to all experience levels.  
We are committed to a safe, professional environment.  
Questions and thoughtful contributions are encouraged.  
Interruptions and grandstanding are not.

[github.com/madison-python/code-of-conduct](https://github.com/madison-python/code-of-conduct)

# Want more Madpy?

[meetup.com/madpython](https://www.meetup.com/madpython/)  
[github.com/madison-python](https://github.com/madison-python)

\bigskip

## Join us on Slack

\bigskip

`slack.madpy.com` to sign up.  
`madpy.slack.com` to sign in.

\bigskip

## Subscribe to our googlegroups

\bigskip

Send a blank email to: `madpy+subscribe@googlegroups.com`

# Madpy meetings

```{r bread, fig.cap="Bread."}
draw_image("img/bread.png", width=0.25)
```

# Annoucements

July 31-August 1: BigDataWisconsin at Marquette ([2018.bigdatawisconsin.org](https://2018.bigdatawisconsin.org))  
August 20: Intro to Python for Data session at Forward Fest  
October 18: AllDayDevOps ([alldaydevops.com](https://alldaydevops.com))

# Madpy calendar

- **July 12: Advanced descriptors: I lied (Jake Zimmerman)**
- August 9: Django! (Willy Hakizimana)
- <s>August 29: Pair Night</s>
- _September 6: Rust for Pythonistas (Josh Karpel)_
- _October 4: JavaScript (Dan) | R and Python (Pierce)_
- _November 8: Ruby through a Python lens (Casey Brant)_
- December 13: ?

# Goings on about town

- La Fete de Marquette
- Art Fair on the Square
- Madison Radicals last home game
